\ttitle

### 2015-06-04 Chapters/Introduction.tex
IntroCPET - HPB changed to liver transplantation and section completed, No studies in HPB as of 2010.

\subsection{Oesophago-gastric Surgery}
\subsection{Colorectal Surgery}
\subsection{Vascular Surgery}
\subsection{Hepato-pancreato-biliary surgery and Transplantation}
Preoperative cardiopulmonary exercise testing is associated with increased 100-day mortality in patients undergoing liver transplantation.\parencite{epstein_aerobic_2004} Patients who undergo liver transplantation have been shown to have improved aerobic capacity a year after surgery. \parencite{iscar_functional_2009} However, there is very little other evidence of the application of cardiopulmonary exercise testing in patients undergoing major hepato-pancreato-biliary surgery or liver transplantation.
\subsection{Thoracic Surgery}

>>>>

\subsection{Oesophago-gastric Surgery}

\subsection{Colorectal Surgery}
\subsection{Vascular Surgery}
\subsection{Liver Transplantation}
Peak $\dot{V}_{O_2}<60\%$ predicted and $\dot{V}_{O_2}AT<50\%$ predicted have been reported to be associated with increased 100-day mortality in patients undergoing liver transplantation. In patients with cirrhosis awaiting hepatic transplantation, reduced aerobic capacity may not only be due to primary cardiorespiratory insufficiency but may also be due to the secondary effects of hepatic dysfunction itself. These include cirrhotic cardiomyopathy, hepatopulmonary syndrome and decreased peripheral oxygen utilisation due to cirrhotic myopathy.\parencite{epstein_aerobic_2004} This is further supported by the fact that patients who undergo liver transplantation have been shown to have improved aerobic capacity a year after surgery. \parencite{iscar_functional_2009} However, there is very little other evidence of the application of cardiopulmonary exercise testing in patients undergoing major hepato-pancreato-biliary surgery or liver transplantation.
\subsection{Thoracic Surgery}
